---
title: "Age VS Singlehood"
---
# Does age affect singlehood? {style="color: #FE4164"}

## General Trend {style="color: black"}
Now, we explore at the marriage status of the population. <br> How many people are **single**? <br>
Is **AGE** a potential factor that affects Singlehood? <br> The graphs below provides further insight.

```{r, echo=FALSE}
suppressMessages(library(ggplot2))

data <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data5.csv")

colnames(data) <- c("Year", "Single_30_39", "Non_Single_30_39")

library(tidyr)
data_long <- gather(data, key = "Status", value = "Percentage", -Year)

ggplot(data_long, aes(x = Year, y = Percentage, fill = Status)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Marriage Status of 30-39 Years", y = "Percentage", x = "Year") +
  scale_fill_manual(values = c("#B76E79", "#FFCCCC"), 
                    labels = c("Non-Single (30-39)", "Single (30-39)")) +
  scale_x_continuous(breaks = unique(data$Year), labels = unique(data$Year)) +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, echo=FALSE}
suppressMessages(library(ggplot2))

data <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data6.csv")

colnames(data) <- c("Year", "Single_40_49", "Non_Single_40_49")

library(tidyr)
data_long <- gather(data, key = "Status", value = "Percentage", -Year)

ggplot(data_long, aes(x = Year, y = Percentage, fill = Status)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Marriage Status of 40-49 Years", y = "Percentage", x = "Year") +
  scale_fill_manual(values = c("#B76E79", "#FFCCCC"), 
                    labels = c("Non-Single (40-49)", "Single (40-49)")) +
  scale_x_continuous(breaks = unique(data$Year), labels = unique(data$Year)) +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))
```
## Singlehood by Age Group {style="color: black"}
For "Singlehood by Age Group" comparison, the data were from the following years:
<br>
10 Year Span: 2013-2022 
<br> 
5 Year Span: 2018-2022
<br>
2 Year Span: 2021-2022
<br>
*_(click below to see the averages of the 2 different age groups)_*
<iframe height="500" width="100%" frameborder="no" src="https://iannnlee.shinyapps.io/IanShinyApp2/"> </iframe>

## Conclusion {style="color: #DE3163"}
Age is also a factor that affects Singlehood. <br> The results have shown that as Age increases, the percentage of Singles in the population decreases. <br> This trend is to be expected as more people will get married as they become older, with increased financial stability and increasing societal pressure to get married. 