---
title: "Qualification Attained VS Singlehood"
---
## Does highest qualification attained affect singlehood? {style="color: pink"}

#### (placeholder) title {style="color: black"}


(placeholder) graph 1
Age VS Relationship Status

(placeholder) graph 2
Highest Qual Attained VS Relationship Status



To make the comparison clearer, I analyses the percentage of singles for the Secondary and University categories. 
```{r, echo=FALSE}
suppressMessages(library("tidyverse"))

clean_data <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data3.csv")

# Filter data for Secondary and University
filtered_data <- clean_data %>%
  select(Year, Secondary, University)

# Define the order of legend labels
legend_order <- c("Secondary", "University")

# Create Plot of Education Level vs Singlehood
ggplot(filtered_data, aes(x = Year)) +
  geom_line(aes(y = Secondary, color = "Secondary")) +
  geom_line(aes(y = University, color = "University")) +
  labs(
    title = "How does Education level affect Singlehood?\n(30-39 Years Old)",  # Use a line break for the title
    x = "Year",
    y = "Singlehood (%)"
  ) +
  scale_color_manual(values = c("Secondary" = "#E48397", "University" = "#5E081E"),
                     breaks = legend_order) +
  scale_x_continuous(breaks = seq(2013, 2022, 1)) +  # Set breaks for the x-axis
  theme_void() +  # Use theme_void() to remove both background grids and grid lines
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 14),  # Adjust the size of the title text
    plot.margin = margin(b = 40, t = 20),
    axis.title.y = element_text(size = 12, angle = 90),  # Make y-axis label vertical
    axis.title.x = element_text(size = 12, angle = 0),
    axis.text = element_text(size = 10),  # Adjust the size of the axis text
    legend.text = element_text(size = 8),  # Adjust the size of the legend text
    legend.title = element_blank(),  # Remove legend title
    legend.spacing.x = unit(0.1, 'cm')  # Adjust spacing between legend items
  )

```
We can see that those that fall under the University category have a higher percentage of singles as compared to Secondary. 

This code: clean data 3, 10 year window 2013-2022
30-39 yr old
```{r, echo=FALSE}
suppressMessages(library("tidyverse"))


clean_data3 <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data3.csv")

# Convert Year to a factor
clean_data3$Year <- as.factor(clean_data3$Year)

# Define the order of legend labels
legend_order <- c("Below Secondary", "Secondary", "Post Secondary", "Diploma & Professional Qualification", "University")

# Love-themed color palette
love_colors <- c("#E4CDD3", "#E48397", "#E24767", "#B51A3A", "#5E081E")

# Create Plot of Education Level vs Singlehood
ggplot(clean_data3, aes(x = Year)) +
  geom_line(aes(y = Below.Secondary, color = "Below Secondary", group = 1)) +
  geom_line(aes(y = Secondary, color = "Secondary", group = 1)) +
  geom_line(aes(y = Post.Secondary..Non.Tertiary., color = "Post Secondary", group = 1)) +
  geom_line(aes(y = Diploma...Professional.Qualification, color = "Diploma & Professional Qualification", group = 1)) +
  geom_line(aes(y = University, color = "University", group = 1)) +
  labs(
    title = "How does Education level affect Singlehood?\n(30-39 Years Old)",  
    x = "Year",
    y = "% of Population, Single"
  ) +
  scale_color_manual(values = setNames(love_colors, legend_order),
                     breaks = legend_order) +
  theme_void() +  
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 14),  # Adjust the size of the title text
    plot.margin = margin(b = 40, t = 20),
    axis.title.y = element_text(size = 10, angle = 90, margin = margin(r = 10)),  # Make y-axis label vertical
    axis.title.x = element_text(size = 10, angle = 0, margin = margin(r = 10)),
    axis.text = element_text(size = 10),  # Adjust the size of the axis text
    legend.text = element_text(size = 7),  # Adjust the size of the legend text
    legend.title = element_blank(),  # Remove legend title
    legend.spacing.x = unit(0.1, 'cm')  # Adjust spacing between legend items
  )
```


This code: clean data 4, 10 year window 2013-2022
40-49 yr old
```{r, echo=FALSE}
clean_data4 <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data4.csv")

# Convert Year to a factor
clean_data4$Year <- as.factor(clean_data4$Year)

# Define the order of legend labels
legend_order <- c("Below Secondary", "Secondary", "Post Secondary", "Diploma & Professional Qualification", "University")

# Love-themed color palette
love_colors <- c("#E4CDD3", "#E48397", "#E24767", "#B51A3A", "#5E081E")

# Create Plot of Education Level vs Singlehood
ggplot(clean_data4, aes(x = Year)) +
  geom_line(aes(y = Below.Secondary, color = "Below Secondary", group = 1)) +
  geom_line(aes(y = Secondary, color = "Secondary", group = 1)) +
  geom_line(aes(y = Post.Secondary..Non.Tertiary., color = "Post Secondary", group = 1)) +
  geom_line(aes(y = Diploma...Professional.Qualification, color = "Diploma & Professional Qualification", group = 1)) +
  geom_line(aes(y = University, color = "University", group = 1)) +
  labs(
    title = "How does Education level affect Singlehood?\n(40-49 Years Old)",  
    x = "Year",
    y = "% of Population, Single"
  ) +
  scale_color_manual(values = setNames(love_colors, legend_order),
                     breaks = legend_order) +
  theme_void() +  
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 14),  # Adjust the size of the title text
    plot.margin = margin(b = 40, t = 20),
    axis.title.y = element_text(size = 10, angle = 90, margin = margin(r = 10)),  # Make y-axis label vertical
    axis.title.x = element_text(size = 10, angle = 0, margin = margin(r = 10)),
    axis.text = element_text(size = 10),  # Adjust the size of the axis text
    legend.text = element_text(size = 7),  # Adjust the size of the legend text
    legend.title = element_blank(),  # Remove legend title
    legend.spacing.x = unit(0.1, 'cm')  # Adjust spacing between legend items
  )
```

to delete: working shiny app <iframe height="600" width="100%" frameborder="no" src="https://iannnlee.shinyapps.io/IanShinyApp/">
</iframe>


<iframe height="400" width="100%" frameborder="no" src="https://iannnlee.shinyapps.io/IanShinyApp2/"> </iframe>


