---
title: "Qualification Attained VS Singlehood"
---

# Does Highest Qualification Attained Affect Singlehood? {style="color: #FE4164"}

## General Trend {style="color: black"}

Firstly, we analyse how Highest Qualification Attained affects Singlehood in the 30-39 year old age group.

```{r, echo=FALSE}
suppressMessages(library("tidyverse"))


clean_data3 <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data3.csv")

clean_data3$Year <- as.factor(clean_data3$Year)

legend_order <- c("Below Secondary", "Secondary", "Post Secondary", "Diploma & Professional Qualification", "University")

love_colors <- c("#E4CDD3", "#E48397", "#E24767", "#B51A3A", "#5E081E")

ggplot(clean_data3, aes(x = Year)) +
  geom_line(aes(y = Below.Secondary, color = "Below Secondary", group = 1)) +
  geom_line(aes(y = Secondary, color = "Secondary", group = 1)) +
  geom_line(aes(y = Post.Secondary..Non.Tertiary., color = "Post Secondary", group = 1)) +
  geom_line(aes(y = Diploma...Professional.Qualification, color = "Diploma & Professional Qualification", group = 1)) +
  geom_line(aes(y = University, color = "University", group = 1)) +
  labs(
    title = "How does Education level affect Singlehood?\n(30-39 Years Old)",  
    x = "Year",
    y = "% of Population, Single"
  ) +
  scale_color_manual(values = setNames(love_colors, legend_order),
                     breaks = legend_order) +
  theme_void() +  
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 14),  
    plot.margin = margin(b = 40, t = 20),
    axis.title.y = element_text(size = 10, angle = 90, margin = margin(r = 10)),   
    axis.title.x = element_text(size = 10, angle = 0, margin = margin(r = 10)),
    axis.text = element_text(size = 10),  
    legend.text = element_text(size = 7),  
    legend.title = element_blank(),  
    legend.spacing.x = unit(0.1, 'cm')  
  )
```

Next, we analyse how Highest Qualification Attained affects Singlehood in the 40-49 year old age group.The general trend is consistent among the 2 age groups. 

```{r, echo=FALSE}
clean_data4 <- read.csv("/Users/iannnlee/Documents/GitHub/iannnlee.github.io/iannnlee.github.io/clean_data4.csv")

clean_data4$Year <- as.factor(clean_data4$Year)

legend_order <- c("Below Secondary", "Secondary", "Post Secondary", "Diploma & Professional Qualification", "University")

love_colors <- c("#E4CDD3", "#E48397", "#E24767", "#B51A3A", "#5E081E")

ggplot(clean_data4, aes(x = Year)) +
  geom_line(aes(y = Below.Secondary, color = "Below Secondary", group = 1)) +
  geom_line(aes(y = Secondary, color = "Secondary", group = 1)) +
  geom_line(aes(y = Post.Secondary..Non.Tertiary., color = "Post Secondary", group = 1)) +
  geom_line(aes(y = Diploma...Professional.Qualification, color = "Diploma & Professional Qualification", group = 1)) +
  geom_line(aes(y = University, color = "University", group = 1)) +
  labs(
    title = "How does Education level affect Singlehood?\n(40-49 Years Old)",  
    x = "Year",
    y = "% of Population, Single"
  ) +
  scale_color_manual(values = setNames(love_colors, legend_order),
                     breaks = legend_order) +
  theme_void() +  
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 14),  
    plot.margin = margin(b = 40, t = 20),
    axis.title.y = element_text(size = 10, angle = 90, margin = margin(r = 10)),  
    axis.title.x = element_text(size = 10, angle = 0, margin = margin(r = 10)),
    axis.text = element_text(size = 10),  
    legend.text = element_text(size = 7),  
    legend.title = element_blank(),  
    legend.spacing.x = unit(0.1, 'cm')  
  )
```

## Comparison between Highest Qualification Attained and Singlehood
The app below provides a clearer comparison between Highest Qualification Attained and Singlehood. <br> Select the age group you would like to view. <br> Then select the Highest Qualification Attained you would like to compare. <br> *_(tick boxes to view)_*

<iframe height="600" width="100%" frameborder="no" src="https://iannnlee.shinyapps.io/IanShinyApp/">

</iframe>

## Conclusion {style="color: #DE3163"}
Highest Qualification Attained proves to be a factor that affects Singlehood. The results have shown that a higher qualification attained generally sees a higher percentage of Singles in the population. This is most evident when comparing Secondary and University. <br> Below Secondary did not have the lowest percentage of Singles. However, this may be skewed due to a smaller sample size, with more people having access to education in Singapore. 
